What is an Ancestral Recombination Graph?

### 2022-03-28 paper.tex

\begin{figure}
\begin{center}
    \includegraphics[width=\textwidth]{illustrations/inference.pdf}
\end{center}
\caption{\label{fig-inferred-args}
ARGs inferred by different methods from a small dataset. Notes about these
ARGs.
}
\end{figure}

>>>>

\begin{figure}
\begin{center}
    \includegraphics[width=\textwidth]{illustrations/inference.pdf}
\end{center}
\caption{\label{fig-inferred-args}
ARGs inferred by different methods from a 2.7kb region of the \textit{Drosophila melanogaster}
ADH locus for 11 samples~\citep{kreitman1983nucleotide}. Note that the position of points on the
Y axis is that chosen for graphical clarity by the graphviz \texttt{dot} algorithm,  rather than being
a direct measure of time. Additional notes about these ARGs.
}
\end{figure}
